Title

### 2024-06-27 paper/main.tex
Updates

In this section, we develop a novel partial measure of association for
mixed data by extending the idea of partial correlation to mixed data. We do
this by combining a mixed-data residualization method with a multivariate
measure of association. Given two variables $ X $ and $ Y $, and a set of
conditional variables $ \bm{Z} $, we are interested in computing an estimate of
the conditional association, $ \rho(X, Y; \bm{Z}) $. If $ \bm{Z} = \emptyset $, we
use a constant value as $ Z $. Firstly, we compute the residuals for $ \bm{x} $ and
$ y $ using the $ \bm{z} $ as the predictor variables. We use the mixed data
residualization approach from \citet{Ankan2023}. We consider each variable type
separately and repeat the following steps for both variables $ X $ and $ Y $:

>>>>

In this section, we define a novel partial measure of association for mixed
data by extending the idea of partial correlation to mixed data. We do this by
combining a mixed-data residualization method with a multivariate measure of
association. Given $ n $ samples $ D = (x, y, \bm{z}) $ of variables $ X $, $ Y $,
and $ \bm{Z} $, we are interested in computing an estimate of the conditional
association $ \rho(X, Y; \bm{Z}) $ between $ X $ and $ Y $ conditioned on $
\bm{Z} $. As the residualization approach requires atleast one conditional
variable to be present, if $ \bm{Z} = \emptyset $, we use a constant value for
$ Z $. Firstly, we compute the residuals for $ X $ and $ Y $ using the $ \bm{Z}
$ as the predictor variables. We use the mixed data residualization approach
from \citet{Ankan2023}. The residual computation depends on the type of 
variable:
